\Huge Conferences in the Era of Expensive Carbon

### 2019-06-04 main.tex
Checkpoint work on writing

In the long term, a carbon price should be uniform across society---i.e., it
should be imposed by governments.  Indeed, many countries and states (e.g.,
California) have already adopted carbon pricing policies; more will follow.
%
Moreover, although the current market price of carbon is still quite low
(around \$15 per ton), experts agree that this will need to rise
significantly over time to achieve the required effect.  Bottom line: We are
entering an era in which carbon is expensive.

@@

A possible short-term response to both questions involves {\em carbon
  offsets}---a tool by which organizations (and individuals) can choose to
voluntarily impose a price on their own emissions.
%
% What they are:
In a nutshell, the idea would be that a conference could raise funds from
registration fees or corporate sponsors and give them, via a carbon offset
{\em vendor}, to someone who will use them to fund an activity (e.g.,
installing methane capture devices on landfill sites or buying efficient
cookstoves to replace open-fire cooking in developing areas) that will avoid
emitting an amount of greenhouse gases equivalent to the emissions from
participants' travel to the conference.
%
\begin{itemize}
\item giving ourselves a ``price signal''
is an effective way to begin raising awareness and changing organizational
behavior.
\item Lots of organizations (universities, companies) are doing this; some
ACM conferences are starting to experiment with voluntary carbon offset fees
at registration time. 
\item There are also some significant
concerns.
\item Concern:
Organizations are not set up to do it.  Our experience with getting
ACM to introduce an offsetting policy shows that it requires significant
effort.
\item Concern: It is hard to choose the price (right now there is an oversupply), and
setting it too low leads to complacency --- it doesn't really bite, so it
doesn't change people's behavior
\item This issue leads many people to argue that offsets "let people off the hook" and encourage
inaction, but we believe it is consistent with encouraging action -- again,
if offsets are priced right.
\end{itemize}

Whether we choose to impose carbon offsets on ourselves or wait for
governments to do it, there are also many things we can do to begin reducing
our footprint.  
\bcp{
  \begin{itemize}
  \item Briefly list a few things we can do (and whose likely effects we'd need data
  to estimate)
  \begin{itemize}
  \item journalize conferences
  \item go virtual
  \item potential parts of a solution: regional conferences, virtual PC
  meetings, virtual participation, mega-conferences
  \end{itemize}
  \item cite our report
  \end{itemize}
}
However, we urgently need to begin gathering and analyzing data, to
better understand the positive and negative effects of any of these
proposals.   
\bcp{Put the discussion of Figure 1 (and an accompanying figure
showing distance traveled to several instances of the same conference) here;
this illustrates the difficulty and the need for careful data gathering and
analysis.} 
All parts of ACM should be doing this kind of analysis.  (The acm-climate
mailing list is one place to exchange ideas about this.)

Ultimately, responding to the inevitability of expensive carbon may involve
rethinking the whole basis of how academic computer science is done.
\bcp{
\begin{itemize}
\item Add a bit of meat about how the current economic model may be
  unsustainable and reworking it will involve substantial organizational
  changes.
\item monitoring and mitigating carbon costs should be an ACM-level activity
\end{itemize}
}

The climate crisis is too large and too urgent to leave it to world leaders
to address at their own pace: organizations at every social scale should
confront their own contributions, raise awareness among their members, and
begin establishing new ways of doing business in the lower-carbon future
that is coming. For ACM, this especially means confronting the
carbon-intensive nature of our conferences.
% %
% You can help accelerate this process in a number of ways: 
% \begin{itemize}
% \item {\bf Get involved} in raising awareness about this issue in the
% organizations you are a part of.  \bcp{Does the rest of this smack of
%   incrementalism?  Maybe delete it.  ``For example, ask the organizers of
%   the conferences you attend what they are doing about reducing or
%   offsetting emissions from participants' travel.''}
% \item {\bf Connect} with others that are engaging with these issues---in
% your workplace, in your other communities, and within ACM (e.g., on the
% {\tt acm-climate} mailing list~\cite{acm-climate}).
% \item {\bf Analyze} your organization's carbon-emitting activities to
% understand how to reduce its footprint now and prepare for the coming era of
% expensive carbon.
% \end{itemize}

\bcp{Things still missing:
  \begin{itemize}
  \item citations for the claims we make (and the carbon-offsets-bad paper
  mentioned by the reviewer)
  \item Go through all the comments and ideas below (including the CACM
  reviews) one last time
  \item Find a place for this: {\tt acm-climate} mailing list~\cite{acm-climate}
  \item Think about adding headings, per Bishop's recommendation

>>>>

In the long term, a carbon price should be uniform across society---i.e., it
should be imposed by governments.  Indeed, many countries\bcp{e.g.?} and
states (e.g., California) have already adopted carbon pricing policies; more
will follow.
%
Bottom line: We are entering an era in which carbon will be expensive.

@@

A possible short-term response to both questions involves {\em carbon
  offsets}---a tool by which organizations (and individuals) can voluntarily
impose a price on their own emissions.
%
% What they are:
In a nutshell, the idea is that a conference can raise funds from
registration fees or corporate sponsors and give them, via a carbon offset
{\em vendor}, to a {\em provider} who will use them to support an activity
(e.g., installing methane capture devices on landfill sites or buying
efficient cookstoves to replace open-fire cooking in developing areas) that
avoids emitting an amount of greenhouse gases equivalent to the emissions
from participants' travel to the conference.
%
\begin{itemize}
\item Lots of organizations (universities, companies) are already doing
this; some ACM conferences are starting to experiment with voluntary carbon
offset fees at registration time.
\end{itemize}

\begin{itemize}
\item There are also some significant
concerns.
\item Concern: Organizations are not set up to do it, and the piecemeal
political and bureaucratic work of designing and implementing a separate
policy for each organization is exhausting.
\item Concern: It is hard to choose the price (right now there is an
oversupply), and setting it too low leads to complacency --- it doesn't
really bite, so it doesn't change people's behavior.  The current market
price of carbon is still quite low (around \$15 per ton), whereas the
``social cost of carbon'' is variously estimated at anywhere from \$40 to
\$400 per ton~\bcp{citation}.
Experts agree that the current price will need to rise significantly
over time to achieve the required effect.
\item This issue leads many people to argue that offsets "let people off the
hook" and encourage inaction, but we believe it is consistent with
encouraging action -- especially if offsets are priced right, but even if
(in the short term) they are too cheap -- because it injects a ``price
signal'' that makes emissions something for planners to optimize.
\item We feel that, on balance, voluntary carbon offsets are an effective
tools for raising awareness and changing organizational behavior in the
short term.
\item Moreover, supporting well-chosen carbon mitigation activities has a
clear benefit and can be done now.
\end{itemize}

Beyond imposing a price on our carbon footprint (or waiting for one to be
imposed from outside), a sane response to climate change should clearly also
include taking steps to reduce the size of this footprint.  
\bcp{
  \begin{itemize}
  \item Briefly list a few things we can do
  \begin{itemize}
  \item journalize conferences
  \item go virtual
  \item potential parts of a solution: regional conferences, virtual PC
  meetings, virtual participation, mega-conferences
  \end{itemize}
  \item cite our report
  \end{itemize}
}
%
However, before we undertake large changes, we need to understand the
situation better.  For most of these ideas, it is hard to confidently
predict either the potential benefits (in terms of reduced emissions) or the
potential costs (to scientific exchange, career development of young
scientists, etc.).  Indeed, a preliminary analysis of registration data from
a number of SIGPLAN conferences paints a rather complicated picture.
%
\bcp{Put the discussion of Figure 1 (and an accompanying figure
showing distance traveled to several instances of the same conference) here;
this illustrates the difficulty and the need for careful data gathering and
analysis.} 
All parts of ACM should be doing this kind of analysis.  (The acm-climate
mailing list is one place to exchange ideas about this.)

Ultimately, responding to the inevitability of expensive carbon may involve
rethinking the whole basis of how academic computer science is done.
\bcp{
\begin{itemize}
\item Add a bit of meat about how the current economic model may be
  unsustainable and reworking it will involve substantial organizational
  changes.  (There may be some good words that we can paraphrase from our
  second reviewer!)
\item monitoring and mitigating carbon costs should be an ACM-level activity
\end{itemize}
}

The climate crisis is too large and too urgent to leave to world leaders to
address at their own pace: organizations at every scale should confront
their own contributions, raise awareness among their members, and begin
establishing new ways of doing business in the lower-carbon future that is
coming.
% For ACM, this especially means confronting the carbon-intensive
% nature of our conferences.
% %
% You can help accelerate this process in a number of ways: 
% \begin{itemize}
% \item {\bf Get involved} in raising awareness about this issue in the
% organizations you are a part of.  \bcp{Does the rest of this smack of
%   incrementalism?  Maybe delete it.  ``For example, ask the organizers of
%   the conferences you attend what they are doing about reducing or
%   offsetting emissions from participants' travel.''}
% \item {\bf Connect} with others that are engaging with these issues---in
% your workplace, in your other communities, and within ACM (e.g., on the
% {\tt acm-climate} mailing list~\cite{acm-climate}).
% \item {\bf Analyze} your organization's carbon-emitting activities to
% understand how to reduce its footprint now and prepare for the coming era of
% expensive carbon.
% \end{itemize}

\bcp{Things still missing:
  \begin{itemize}
  \item citations for the claims we make (and the carbon-offsets-are-bad paper
  mentioned by the reviewer)
  \item Go through all the comments and ideas below (including the CACM
  reviews) one last time
  \item Find a place for this: {\tt acm-climate} mailing list~\cite{acm-climate}
  \item Think about adding headings, per Bishop's recommendation
